---
title: "bricks with data dependencies"
output: rmdformats::readthedown
vignette: >
  %\VignetteIndexEntry{brick-dependencies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{css styling, echo=F}
.code{
  background-color:black;
  color:#41FF00;
}
```
```{r helpers, echo=F}
library(biobricks)
build.sh <- \(wd){
  \(txt,args=c(),print=F,...){ # create shell with workdir
    cmd <- do.call("sprintf",as.list(c(txt,args)))
    cmd <- paste("cd ",wd,";",cmd,collapse="")
    
    if(print){ system(cmd,intern=T,...) |> cat(sep="\n") }
    else{      system(cmd,ignore.stdout=T,ignore.stderr=T,...) }
}}
```

# Create a new bblib
We create a temporary bblib for testing
```{r new.bblib, class.output="code", message=F}
bblib <- local_bblib()
bbsh  <- build.sh(wd=bblib) # shell w/ workdir = bblib
bbsh("tree -a -L 1", print=T)
```

## Install hello-brick
```{r install, class.output="code"}
install_biobricks("hello-brick")
bbsh("tree -a --filelimit 4",print=T)
```

The install hello brick uses `$bblib/cache` for it's cache directory
```{r view.config, class.output="code"}
bbsh("cat biobricks-ai/hello-brick/.dvc/config",print=T)
```

## Pull hello-brick
Pulling hello-brick  
```{r pull.hello, class.output="code"}
brick_pull("hello-brick")
bbsh("tree biobricks-ai/hello-brick/data",print=T)
```

# Set up a new project
```{r new.project, class.output="code", message=F}
dbrick <- withr::local_tempdir()
sh     <- build.sh(wd=dbrick)
sh("git init")
sh("dvc init")
sh("tree -a -L 1", print=T)
```

## biobricks cache
Add the shared biobricks cache
```{r create.cache, class.output="code"}
sh('dvc cache dir $bblib/cache')
sh('dvc config cache.shared group')
sh('dvc config cache.type symlink')
sh('cat .dvc/config',print=T)
```

## import hello-brick
To add imports, create an imports directory and use `dvc import`
```{r message=F, class.output="code"}
sh("mkdir imports")
sh("dvc import -o imports/hello-brick git@github.com:biobricks-ai/hello-brick data")
sh("tree", print=T)
```

## a new pipeline
Create a new dvc.yaml with dependencies on hello-brick
```{r, class.output="code"}
dvc.yaml <- list(
  stages = list(
    depbrick = list(
      cmd  = "cp imports/hello-brick/mtcars.parquet ./data/mtcars2.parquet",
      deps = list("imports/hello-brick/mtcars.parquet"),
      outs = list("data/mtcars2.parquet")
    ))) |> yaml::as.yaml()

cat(dvc.yaml,file=fs::path(dbrick,"dvc.yaml"))
sh("cat dvc.yaml",print=T)
```

## Run the pipeline
```{r run.pipe, class.output="code"}
sh("mkdir data")
sh("dvc repro",print=T)
```
